### 2016-02-24 Docs/managing_jobs/managingjobs.tex
more compiler info
more slurm
add note about PGI 16

The \boxlib\ floating point exception trapping is disabled with PGI compilers, due to 
problems with PGI using the system header files.

@@

@@

\subsection{General Guidelines}

@@

>>>>

The \boxlib\ floating point exception trapping is disabled with PGI
compilers earlier than version 16, due to problems with PGI using the
system header files.  From version 16 onward, things should work.

@@

\item Intel 16.x currently has issues with the linear solvers in \boxlib\
  and should be avoided.

@@

\subsection{Running Jobs}

@@

Jobs are submitted with {\tt sbatch}.  A job can be canceled using {\tt scancel}, and
the status can be checked using {\tt squeue -u {\em username}}.
